---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# reedsol

The goal of reedsol is to sample from a Reed-Solomon distribution using rejection sampling.

## Installation

You can install the development version of reedsol from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("mightymetrika/reedsol")
```

## Example

Sample using reedsol_sim() as follows:

```{r example}
library(reedsol)

reedsol_sim(data = c(2, 4, 6),
            n = 5,
            q = 8)
```


## Parameters

* data: A numeric vector used to generate the Reed-Solomon curve.
* n: Number of samples to generate (default: 1)
* q: Size of the finite field GF(q) (default: 256)
* k: Degree of the polynomial to use (default: length of data)

## Description

The function works by:

1. Converting input data to elements in GF(q)
2. Constructing a probability density function as a polynomial with coefficients from the data
3. Normalizing this function through numerical integration
4. Using rejection sampling to generate random samples
